Inferring Graphics Programs from Images

### 2017-05-09 paper.tex
Comments.

@@

\textbf{Comment for reader: this paragraph is a little grandiose and goes
  beyond what we've actually done. But these are the kinds of things
  that motivate the work, and I think that in some form these ideas
  should be in the introduction or the conclusion.} How could an agent go from noisy,
high-dimensional perceptual input to a symbolic, abstract object, like
a computer program?  Here we consider this problem within the context
of \emph{graphics program synthesis}.  We develop an approach for
converting natural images, such as hand drawings, into executable
source code for drawing the original image.
The source code captures not just the objects in the image,
but also describes their geometric relationships.

High dimensional perceptual input is ill matched to the abstract
semantics of a programming language. But programs with constructs like
recursion or iteration produce a simpler \emph{execution trace} of
primitive actions. Our hypothesis is that the execution trace of the
program is better aligned with the perceptual input, and that the
trace can act as a kind of bridge between perception and programs. We
test this hypothesis by developing a model that learns to map from an
image to the execution trace of the graphics program that drew it.
With the execution trace in hand, we can bring to bear techniques from
the program synthesis community to recover the latent graphics program.

@@

We develop a hybrid architecture for inferring graphics programs.  Our
approach uses a deep network infer an execution trace from an image;
this recovers primitive drawing operations like lines, circles, or
arrows.  For added robustness we use the deep network as a proposal
distribution for a stochastic search over execution traces.
Finally we use techniques in the program synthesis community to
recover the program from its trace.

Each of these three components -- the deep network, the stochastic
search, the program synthesizer -- confers its own advantages. From
the deep network we get a very fast system that can recover plausible
execution traces in about a minute. From the stochastic search we get
added robustness; essentially the stochastic search can correct
mistakes made by the deep network's proposals.  From the program
synthesizer we get abstraction: our system recovers coordinate
transformations, for loops, and subroutines, which are useful for
downstream tasks.

@@

Figure~\ref{architecture} illustrates this architecture.  We first
pass the target image and a rendering of the trace so far to a
convolutional network. Given the features extracted by the
convolutionional network, a multilayer perceptron then predicts a
distribution over the next drawing command to add to the trace.  We
predict the drawing command token-by-token, and condition each token
both on the image features and on the previously generated tokens.
For example, the network first decides to emit the \verb|CIRCLE| token
conditioned on the image features, then it emits the $x$ coordinate of
the circle conditioned on the image features and the \verb|CIRCLE|
token, and finally it predicts the $y$ coordinate of the circle
conditioned on the image features, the \verb|CIRCLE| token, and the
$x$ coordinate.

@@

We train the network by sampling execution traces $T$ and target
images $I$ for randomly generated scenes, and maximizing
(\ref{objective}) wrt $\theta$ by gradient ascent. Despite the
architecture being recurrent, training is fully supervised. In a
sense, this model is like an autoregressive variant of AIR. When we
have the generative model (the rendering function) and treat the trace
as fully observed, we need not solve an unsupervised or reinforcement
learning problem.

@@

%  \node at (canvas.x,canvas.y) {Canvas};
\end{tikzpicture}
\caption{Our neural architecture for inferring the execution trace of a graphics program from its output.}  \label{architecture}
  \end{figure}

>>>>

\newcommand{\remark}[1]{\textcolor{red}{[#1]}}

@@

\textbf{Comment for reader: this paragraph is a little grandiose and goes
  beyond what we've actually done. But these are the kinds of things
  that motivate the work, and I think that in some form these ideas
  should be in the introduction or the conclusion.} How could an agent go from noisy,
high-dimensional perceptual input to a symbolic, abstract object, like
a computer program?  Here we consider this problem within the context
of \emph{graphics program synthesis}.  We develop an approach for
converting natural images, such as hand drawings, into executable
source code for drawing the original image.
\remark{The use of `graphics programs / visual programs' in the paper title, title of this section, and the body of this section feels too broad. `Graphics program' could conjur a lot of different ideas (esp. 3D graphics); don't want to set the reader up to expect one thing and then be disappointed that what you've done isn't that. You bring up diagram-drawing later in the intro; I think it should be made clear sooner (and certainly mentioned explicitly in the abstract, when you get around to writing that).}

\newcommand{\exampleImageSize}{2cm}
\begin{figure}[h]
  \begin{minipage}[t]{0.8\linewidth}  
\begin{tabular}{llll}
  \includegraphics[width = \exampleImageSize]{figures/expert-60.png}&
  \includegraphics[width = \exampleImageSize]{figures/expert-5.png}&
    \includegraphics[width = \exampleImageSize]{figures/expert-17.png}&
    \includegraphics[width = \exampleImageSize]{figures/expert-58.png}\\
  \includegraphics[width = \exampleImageSize]{figures/60.png}&
  \includegraphics[width = \exampleImageSize]{figures/5.png}&
    \includegraphics[width = \exampleImageSize]{figures/17.png}&
    \includegraphics[width = \exampleImageSize]{figures/58.png}
\end{tabular}
\subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.2\linewidth}
    \begin{tikzpicture}
      \node(picture) at (0,0) {\includegraphics[width = 2cm]{figures/expert-31.png}};
      \draw[very thick,->] (picture.south)  -- (0,-2);
    \end{tikzpicture}
    \texttt{FOR} $0\leq i\leq 3$:\\
    \texttt{RECTANGLE} $()$\\
    \texttt{FOR} $0\leq j < i$:\\
    \texttt{CIRCLE} $()$\\
    \subcaption{}
  \end{minipage}
  \caption{(a): Model parses hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}
  \end{figure}

High dimensional perceptual input is ill matched to the abstract
semantics of a programming language. But programs with constructs like
recursion or iteration produce a simpler \emph{execution trace} of
primitive actions. Our hypothesis is that the execution trace of the
program is better aligned with the perceptual input, and that the
trace can act as a kind of bridge between perception and programs. We
test this hypothesis by developing a model that learns to map from an
image to the execution trace of the graphics program that drew it.
With the execution trace in hand, we can bring to bear techniques from
the program synthesis community to recover the latent graphics program.
\remark{This is an \emph{excellent} explanation! I would add maybe one more sentence / citation to elaborate on what you mean by `techniques from the program synthesis community', as this will be an unfamiliar concept to some readers, I imagine.}

@@

We develop a hybrid architecture for inferring graphics programs.  Our
approach uses a deep neural network infer an execution trace from an image;
this network recovers primitive drawing operations such as lines, circles, or
arrows~\remark{and their parameters?}
. For added robustness, we use the deep network as a proposal
distribution for a stochastic search over execution traces.
Finally, we use techniques in the program synthesis community to
recover the program from its trace.
\remark{This paragraph is all about making things a bit more specific, so you really need more specifics about program synth here.}

Each of these three components -- the deep network, the stochastic
search, the program synthesizer -- confers its own advantages. From
the deep network, we get a very fast system that can recover plausible
execution traces in about a minute~\remark{A minute seems slow to me, for deep net inference. Are you talking about training time, here, or...?}. From the stochastic search we get
added robustness; essentially, the stochastic search can correct
mistakes made by the deep network's proposals.  From the program
synthesizer, we get abstraction: our system recovers coordinate
transformations, for loops, and subroutines, which are useful for
downstream tasks~\remark{and can help correct some mistakes of the earlier stages?}.
\remark{I wonder if this would work even better as a bulleted list...}

@@

Figure~\ref{architecture} illustrates this architecture.  We first
pass the target image and a rendering of the trace so far to a
convolutional network. Given the features extracted by the
convolutionional network, a multilayer perceptron then predicts a
distribution over the next drawing command to add to the trace.  We
predict the drawing command token-by-token, and condition each token
both on the image features and on the previously generated tokens.
For example, the network first decides to emit the \verb|CIRCLE| token
conditioned on the image features, then it emits the $x$ coordinate of
the circle conditioned on the image features and the \verb|CIRCLE|
token, and finally it predicts the $y$ coordinate of the circle
conditioned on the image features, the \verb|CIRCLE| token, and the
$x$ coordinate.
\remark{There are some more details that are important to provide about this architecture, though possibly in an Appendix: the functional form(s) of the probability distributions over tokens, the network layer sizes, which MLPs share parameters, etc.}

\remark{Planning to move the description of SMC / beam search up here, too?}

@@

We train the network by sampling execution traces $T$ and target
images $I$ for randomly generated scenes, and maximizing
(\ref{objective}) wrt $\theta$ by gradient ascent. Despite the
architecture being recurrent, training is fully supervised. In a
sense, this model is like an autoregressive variant of AIR.
\remark{I like that you make this connection, but it could be made more precisely. Specifically, (1) the architecture isn't \emph{really} recurrent (it uses no hidden state cells), so it'd be good to use a different term or drop this part of the point: (2) training of recurrent nets is also typically fully-supervised (Most RNNs lack latent variables per timestep)---if you're thinking about AIR specifically, maybe just say that, and (3) it's like an autogressive AIR \emph{without attention}.}
\remark{Something related to this that's also cool to point out: training this model doesn't require backpropagation across the entire sequence of drawing commands (drawing to the canvas `blocks' the gradients, effectively offloading memory to an external (visual) store, so in principle it might be scalable to much longer sequences.}

%% When we
%% have the generative model (the rendering function) and treat the trace
%% as fully observed, we need not solve an unsupervised or reinforcement
%% learning problem.

@@

%  \node at (canvas.x,canvas.y) {Canvas};
\end{tikzpicture}
\caption{Our neural architecture for inferring the execution trace of a graphics program from its output.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me). (2) Are the target image / canvas convolved down independently, or jointly (i.e. starting as a 2-channel image)? That's an important detail that's not clear with the current figure/explanation. (3) The three circles downstream from `Image Features' are supposed to be MLPs, I assume(?), but it took me a little while to parse that. Having some visual way of clearly separating network operations from data (color, perhaps) would go a long way.}}  \label{architecture}
  \end{figure}
